Learning Network Size while Training with ShrinkNets

### 2018-02-09 paper/ICML/approach.tex
edits

In this section we present the \emph{Switch layer}, a core concept of our
ShrinkNets approach that allows to learn the network size as part of the
training process. Then, we explain how to adapt the training procedure to
support the new layer. We begin with a high-level overview of our method.

@@

At a high-level, the ShrinkNets approach consists of two interconnected stages.
The first stage is concerned with identifying neurons that are not contributing
to increasing the prediction accuracy of the network and deacivate them. The
second stage is concerned with actually removing the neurons from the network
and shrinking its size, therefore leading to faster inference times. We give an
overview of both processes next:

>>>>

In this section describe the
ShrinkNets approach, which allows us to learn the network size as part of the
training process. The key idea is the addition of 
\emph{switch layers} added after each layer in the network;  these 
layers allow us to disable certain neurons during training.
 Once we've introducd the basic method, we
 explain how to adapt the training procedure to
support this new layer. %We begin with a high-level overview of our method.

@@

At a high-level, the ShrinkNets approach consists of two interconnected stages.
The first stage identifies neurons that do not contribute
to increasing the prediction accuracy of the network and deacivate them. The
second stage is concerned with actually removing the neurons from the network
and shrinking its size, therefore leading to faster inference times. We give an
overview of both processes next:

### 2018-02-09 paper/ICML/introduction.tex
Improve plots and multiple small changes
edits

As neural networks become increasingly widely deployed in a variety of
applications  -- ranging from improving camera quality on mobile phones
\cite{googleapple} to language translation \cite{languagetranslation} to text
auto-completion \cite{autocomplete} -- and on diverse hardware architectures
-- from laptops to phones to embedded sensors --  inference performance and
model size are becoming equally as important as  traditional measures of
prediction quality. However, these three aspect of model performance --
quality, performance and size -- are largely optimized separately today, often
with suboptimal results.

Of course, the problem of finding compressed or small networks is not new.
Existing techniques typically aim make a pre-trained neural network smaller
\cite{something1,something2} by taking one of two approaches:  either by
applying quantitazation \cite{quant} or code compilation~\cite{something}
techniques that can be applied blindly to any network, or they analyze the
structure of the network and systematically prune
connections~\cite{han2015deepcompression,Cun} or neurons~\cite{XXX}
based on some loss function.  Although these techniques can substantially
reduce model size, they have several drawbacks.  First, they often negatively
impact model quality.  Second, they can (surprisingly) negatively impact
inference time as they transform dense matrix operations into sparse ones,
which can be substantially slower to execute on modern hardware
\cite{something}, especially GPUs which do not efficiently support sparse
linear algebra.  Third, these techniques generally start by optimizing
particular architecture for prediction performance, and then, as a post-
processing step, apply compression  to generate a smaller model that meets the
resource constraints of the   deployment setting.  Because the network
architecture is essentially fixed during compression,   model architectures
that work better in small settings may be missed -- this is especially true in
large networks like many- layered CNNs,  where it is infeasible to try explore
even a small fraction of possible network configurations.

@@

In contrast, in this paper we present a new method to simultaneously optimize
both network size and model performance. The key idea is to learn the right
network size at the same time that we optimize for prediction performance. Our
approach, called {\it ShrinkNets}, starts with an {\it oversized} network, and
dynamically shrinks it by eliminating neurons during training time.  Our
approach has two main benefits.  First, we explore the architecture of models
that are both small and perform well, rather than starting with a high-
performance model and making it small.  This allows us to efficiently generate
a family of smaller and accurate models without an exhaustive and expensive
hyperparameter search over the number of neurons in each layer. Second, in
contrast to existing neural network compression techniques~\cite{Aghasi2016,han2015deepcompression}, our approach results in models that are both
not only small, but where the  layers are dense, which means that inference
time is also improved, e.g., on GPUs.

@@

In summary, our contributions are as follows: 
\begin{compactenum}
\item We propose a novel technique based on dynamically switching on and off neurons, 
which allows us to optimize the network size as the network is trained. 
\item We show that our technique is a relaxation\mpv{?} of group sparsity and 
prove \mpv{fill in}. 
\item \srm{Some claim about model size vs performance}
\item We demonstrate the efficacy of our technique on both convolutional and fully-connected neural nets,
showing that 
ShrinkNets finds networks within +/-X\% of best hand-crafted accuracy in XX\% of
training time compared to existing hyperparameter optimization methods.
\item We also demonstrate that ShrinkNets can achieve this accuracy with only YY\% 
of neurons.
\item \srm{Something about dense networks and then benefit over optimal brain damage}
\item \srm{Some claim about inference time}
\item \srm{Some claim about compatibility with existing compression techniques?}
\end{compactenum}

>>>>

As neural networks become increasingly widely deployed in a variety of
applications  -- ranging from improving camera quality on mobile phones
\cite{googleapple} to language translation \cite{languagetranslation} to text
auto-completion \cite{autocomplete} -- and on diverse hardware architectures
-- from laptops to phones to embedded sensors --  inference performance and
model size are becoming as important in learning as metrics measures of
prediction quality. However, these three aspect of model performance --
quality, performance and size -- are largely optimized separately today, often
with suboptimal results.

Of course, the problem of finding compressed or small networks is not new.
Existing techniques typically aim make a pre-trained neural network smaller
\cite{something1,something2} by taking one of two approaches:  either by
applying quantization \cite{quant} or code compilation~\cite{something}
techniques that can be applied blindly to any network, or by analyzing the
structure of the network and systematically pruning
connections~\cite{han2015deepcompression,Cun} or neurons~\cite{XXX}
based on some loss function.  Although these techniques can substantially
reduce model size, they have several drawbacks.  First, they often negatively
impact model quality.  Second, they can (surprisingly) negatively impact
inference time as they transform dense matrix operations into sparse ones,
which can be substantially slower to execute on modern hardware
\cite{something}, especially GPUs which do not efficiently support sparse
linear algebra.  Third, these techniques generally start by optimizing a
particular architecture for prediction performance, and then, as a post-
processing step, applying compression  to generate a smaller model that meets the
resource constraints of the deployment setting.  Because the network
architecture is essentially fixed during this post-processing,   model architectures
that work better in small settings may be missed -- this is especially true in
large networks like many-layered CNNs,  where it is infeasible to try explore
even a small fraction of possible network configurations.

@@

In contrast, in this paper we present a new method to simultaneously optimize
both network size and model performance. The key idea is to learn the right
network size at the same time that we optimize for prediction performance. Our
approach, called {\it ShrinkNets}, starts with an {\it oversized} network, and
dynamically shrinks it by eliminating neurons during training time.  Our
approach has two main benefits.  First, we explore the architecture of models
that are both small and perform well, rather than starting with a high-
performance model and making it small.  This allows us to efficiently generate
a family of smaller and accurate models without an exhaustive and expensive
hyperparameter search over the number of neurons in each layer. Second, in
contrast to existing neural network compression techniques~\cite{Aghasi2016,han2015deepcompression}, our approach results in models that are
not only small, but where the  layers are dense, which means that inference
time is also improved, e.g., on GPUs.

@@

In summary, our contributions are as follows: 
\begin{compactenum}
\item We propose a novel technique based on dynamically switching on and off neurons, 
which allows us to optimize the network size as the network is trained. 
\item We show that our technique is a relaxation of group LASSO~\cite{Yuan2006} and prove that our problem admits many global minima.
\item \srm{Some claim about model size vs performance}
\item We demonstrate the efficacy of our technique on both convolutional and fully-connected neural nets,
showing that 
ShrinkNets finds networks within +/-X\% of best hand-crafted accuracy in XX\% of
training time compared to existing hyperparameter optimization methods. \srm{Mention the specific 
model/dataset where this is true.}
\item We demonstrate that ShrinkNets can achieve this accuracy with only YY\% 
of neurons. \srm{This claim should be something about how much smaller a network with say 99\%
accuracy is one some real dataset}
\item \srm{Something about dense networks and then benefit over optimal brain damage}
\item \srm{Some claim about inference time}
\item \srm{Some claim about compatibility with existing compression techniques?}
\end{compactenum}
